RNA-seq from 4 cell populations

### 2020-08-21 deconvolution/fans4/molec_profiling.Rmd
Initial commit

isexpr = rowSums(cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)

@@

geneExprCombined = cpm(dge, log=TRUE)

@@

    isexpr = rowSums(cpm(geneCountSub[,idx])>1) >= 0.3*ncol(geneCountSub[,idx])
    table(isexpr)

>>>>

isexpr = rowSums(edgeR::cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)

@@

geneExprCombined = edgeR::cpm(dge, log=TRUE)

@@

    isexpr = rowSums(edgeR::cpm(geneCountSub[,idx])>1) >= 0.3*ncol(geneCountSub[,idx])
    table(isexpr)
